Second Language Acquisition: Exploring Common Mistakes

### 2021-06-22 paper.Rmd
Update glmer

In order to save on computational resources, I take only 1% of the data saving the share of `correct` and `incorrect` entries.

```{r}
# # uncomment if there is no data/sample_df.csv file.
# sample_df <- df %>%
#   slice_sample(prop = 0.01)
# 
# write_csv(sample_df, 'data/sample_df.csv', append = FALSE)
```

```{r, result='markup'}
sample_df <- read_csv("data/sample_df.csv", 
                      col_types = cols('f','i','i',
                                       'c','f','c',
                                       'f','f','d',
                                       'f','f','f',
                                       'i','i'))

sample_df %>% 
  group_by(label) %>% 
  summarise(n()) %>% 
  left_join(df %>% 
              select(label) %>%
              group_by(label) %>% 
              summarise(n()), by='label') %>% 
  knitr::kable(col.names = c("Label", 'Sample', 'Total'),
               align = c('c','r', 'r'),
               caption = "Number of entries by label")
```

@@

All the models are very close and inefficient. Some improvement comes from a random effect by token itself but not enough.

```{r, results='markup'}
summary(lmer5)
```

@@

anova(lmer5, lmer9, lmer10, lmer11)
```
Model 9 `label ~ format + format:client + (1 | token)` looks more promising, yet it is still inefficient.

@@

```{r, result='markup'}
summary(lmer11)
```

This set of feature does not provide any imporvement as well. For now and based on Chapter 2.3, it seems that choosing `correct` when a task format is `reverse_tap` is the most promising approach. Especially if grouped by the position of a token in a sentence.

>>>>

In order to save on computational resources, I take only 10% of the data saving the share of `correct` and `incorrect` entries.

```{r}
# # uncomment if there is no data/sample_df.csv file.
# sample_df <- df %>%
#   slice_sample(prop = 0.1)
# 
# write_csv(sample_df, 'data/sample_df.csv', append = FALSE)

sample_df <- read_csv("data/sample_df.csv", 
                      col_types = cols('f','i','i',
                                       'c','f','c',
                                       'f','f','d',
                                       'f','f','f',
                                       'i','i'))
```

```{r, results='markup'}
sample_df %>% 
  group_by(label) %>% 
  summarise(Sample = n()) %>% 
  left_join(df %>% 
              select(label) %>%
              group_by(label) %>% 
              summarise(Dataset = n()), by='label') %>% 
  knitr::kable(caption="Distribution of correct and incorrect entries")
```

@@

All the models are very close and inefficient.

```{r, echo=TRUE, results='markup'}
summary(lmer5)
```

Some improvement comes from a random effect by token itself but not enough.

@@

anova(lmer5, lmer9, lmer10, lmer11)
```
Even a slightly more complex model like `label ~ format + format:client + (1 | token)` fail to converge.

@@

This set of feature does not provide much improvement. For now and based on Chapter 2.3, it seems that choosing `correct` when a task format is `reverse_tap` is the most promising approach. Especially if grouped by the position of a token in a sentence.
